Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-18 ConferencePaper/DraftEdwardsWoods.Rnw
Getting the mulinom in the paper

<<OrthodoxStructTenure,echo=FALSE,results=tex>>=

>>>>

<<OrthodoxStructTenure,echo=FALSE,results=verbatim>>=
# Recreating what Edwards did in Stata
#Output is not pretty  ***TODO Make Output pretty ***
# mlogit owndwel rentass totsqft_en lnincome nhsldmem reporttot i.education i.householder_race#c.reporttot urbanrural, base(1)
library(nnet)
OrthodoxStructTenure<-multinom(StrTenure~ RENTHELP+TOTSQFT_EN+Income+NHSLDMEM+ reporttot+EDUCATION+reporttot+reporttot:EthRace+UR,data=RECS)
summary(OrthodoxStructTenure)
#xtable(summary(OrthodoxStructTenure),caption="Orthodox Structure and Ownership Model",label="tab:OrthoStructTenure")
@
